```{r, include = FALSE}
source(here::here("setup.R"))
for (file in list.files(here::here("R"), full.names = TRUE)) source(file)
```

# Reading the data

* The format of signal files is `<sensor>_exp<XX>_user<YY>.txt`, where `<sensor>` is either `acc` (accelerometer) or `gyro` (gyroscope), `<XX>` is experiment ID, and `<YY>` is user ID.
* Each signal file contains three columns, one for each sensor channel, corresponding to the *X*, *Y*, and *Z* directions. The file consists of a sequence of samples.
* Instead of labeling every time point, the `labels_train.txt` file lists time intervals: each interval has a `start`, `end`, and activity code `act_code` (numbered 1 through 12).
* These intervals correspond to segments of the signals in `acc_expXX_userYY.txt` and `gyro_expXX_userYY.txt`.
* The names of activity codes are stored in the file `activity_labels.txt`.

**Goal:** To analyze the data, we need to merge the signals with their activity code and labels.
In practice, this means reading the signals (each row = one time point) and assigning the correct label to each time point.

## Import Activity labels

```{r}
# Import the activity labels file
act_labels <- read.table(
  file.path(data_dir, "activity_labels.txt"),
  header = FALSE, col.names = c("code", "activity")
)

# Import the train labels file that contains the activity intervals for each trial and user
labels0 <- read_delim(file.path(train_dir, "labels_train.txt"),
  delim = " ",
  col_names = c("trial", "userid", "act_code", "start", "end"), col_types = "iiiii"
)

# Join the activity labels to the labels data frame
labels <- labels0 |> left_join(act_labels, by = c(act_code = "code"))

# Expand the labels data frame to have one row per sample
sample_labels <- labels |>
  mutate(segment = row_number()) |> # identify each separate activity interval
  reframe(
    sampleid = seq.int(start, end), # expand start:end into all sample IDs
    .by = c(trial, userid, act_code, activity, segment)
  )

# Check the result
cat("The sample_labels data frame has", nrow(sample_labels), "rows and", ncol(sample_labels), "columns.\n")
head(sample_labels)
tail(sample_labels)
```

## Import the signals

To begin, we'll focus on 2 single files: the accelerometer and gyroscope signals for participant `user01` in trial `exp01`.

```{r, fold = "Relevant functions", code = readLines(here::here("R", "data.R"))}
source(here::here("R", "data.R"))
```

```{r}
username <- 1
expname <- 1

# Load the accelerometer signal for user01 in exp01
file_path_acc <- get_file_path(train_dir, "acc", expname, username)
acc_signal <- load_signal(file_path_acc)

# Load the gyroscope signal for user01 in exp01
file_path_gyro <- get_file_path(train_dir, "gyro", expname, username)
gyro_signal <- load_signal(file_path_gyro)
```

## Merging Signals and Labels

We create a tibble that contains the `userid`, the `trial` number, and a `sampleid` for each row in a signal df.
Then we bind in the three signal columns (`X1`, `X2`, `X3`) and finally (left) join this table with `sample_labels`
so that every sample has the correct activity label.

```{r}
# Create a data frame with the signal and the corresponding activity labels
acc_df <- get_signal_df(expname, username, acc_signal, sample_labels)
gyro_df <- get_signal_df(expname, username, gyro_signal, sample_labels)

# Check the result (first few rows are not interesting; the following are)
cat("Accelerometer data frame for user", username, "in trial", expname, "\n")
print(acc_df[1227:1239, ])
cat("Gyroscope data frame for user", username, "in trial", expname, "\n")
print(gyro_df[1227:1239, ])
```

This table is exactly what we need: each sample in the three signal channels is now labeled with its corresponding activity.

To check if the labeling is correct, we can visualize the result.

```{r}
options(repr.plot.width = 15) # widen the plot for readability

plot_signal_df <- function(x) {
  x %>%
    filter(!is.na(activity)) %>% # keep only labeled samples
    ggplot(aes(x = sampleid, y = X1, colour = factor(activity), group = segment)) +
    geom_line()
}

# Plot the first signal channel for acc, colored by activity
plot_signal_df(acc_df)
```

```{r}
# Plot the first signal channel for gyro, colored by activity
plot_signal_df(gyro_df)
```

## Epochs

We also need an activity label for each epoch. Most epochs will have 128 samples with one and the same activity label.
However, because the partitioning of the signals into epochs of 128 samples is done without regard for the activity label,
some epochs will have more than one activity label, for example for a change in activity during that epoch.
We will deal with that by labeling such epochs with the label that is associated with the largest number of samples of that epoch.

Additionally, we will compute a confidence score for the activity label of each epoch,
which is the proportion of samples in that epoch that have the most common activity label.

**Each epoch becomes one row in a tidy data frame, with features that summarise the signal in that epoch.**

```{r, fold = "Relevant functions", code = readLines(here::here("R", "segmentation.R"))}
source(here::here("R", "segmentation.R"))
```

```{r, include = FALSE}
saveRDS(sample_labels, file.path(output_dir, "sample_labels.rds"))
saveRDS(acc_df, file.path(output_dir, "acc_df.rds"))
saveRDS(gyro_df, file.path(output_dir, "gyro_df.rds"))
```
