```{r, include = FALSE}
source(here::here("setup.R"))
for (file in list.files(here::here("R"), full.names = TRUE)) source(file)
acc_df <- readRDS(file.path(output_dir, "acc_df.rds"))
gyro_df <- readRDS(file.path(output_dir, "gyro_df.rds"))
```

# Time domain features

## Histograms

Histograms give a detailed picture of the distribution of the signal values.
For instance, have a look at the histograms of the signal samples per activity:

```{r}
plot_signal_df_hist <- function(x) {
  x |>
    filter(!is.na(activity)) %>% # keep only labeled samples
    ggplot(aes(X1)) +
    geom_histogram(bins = 40, fill = 1, alpha = 0.5) +
    geom_histogram(aes(X2), bins = 40, fill = 2, alpha = 0.5) +
    geom_histogram(aes(X3), bins = 40, fill = 4, alpha = 0.5) +
    facet_wrap(~activity, scales = "free_y")
}

# Plot a histogram of the accelerometer signal, separated by activity
plot_signal_df_hist(acc_df)
```

```{r}
# Plot a histogram of the gyroscope signal, separated by activity
plot_signal_df_hist(gyro_df)
```

**The histograms for different activities look quite distinct.** This means that statistical summaries
(mean, standard deviation, skewness, etc.) could help us tell the activities apart.

* the center (mean),
* the spread (standard deviation, interquartile range, min-max range),
* the shape (skewness, kurtosis),
* ...and so on.

## Feature extraction

```{r, fold = "Relevant functions for segmentation of activities", code = readLines(here::here("R", "segmentation.R"))}
source(here::here("R", "segmentation.R"))
```

```{r, fold = "Relevant functions for time domain feature extraction", code = readLines(here::here("R", "features_time.R"))}
source(here::here("R", "features_time.R"))
```

```{r}
# Compute features per epoch for acc
time_features_acc <- get_time_domain_features(acc_df)
head(time_features_acc)

# Compute features per epoch for gyro
time_features_gyro <- get_time_domain_features(gyro_df)
head(time_features_gyro)

# Plot the confidence levels for each activity label
time_features_gyro |>
  filter(aggr_activity != "-") |>
  ggplot(aes(x = aggr_activity, y = activity_confidence)) +
  geom_boxplot() +
  facet_wrap(~aggr_activity, scales = "free_x") +
  theme(axis.text.x = element_blank()) +
  labs(x = "Activity label", y = "Confidence of activity label")
```

This is a tidy data frame that can be used in the classification algorithms discussed in chapters 3 and 4 of ISLR.

***Note**: You may not be familiar with the `AR1.1`, `AR1.2` and `AR12.1` computed above.
These are called _autocorrelations_ (at lags 1 and 2) and _lagged cross-correlations_.
They are discussed in [Feature Extraction from Signals](https://paper.dropbox.com/doc/Feature-extraction-from-Signals--A62tmtXDMS34X292NP0fKphQAQ-qCp5uvj47gmyuw5nmB8lL).
They are interesting because slowly changing signals have high autocorellations, while fast changing signals have low or even negative autocorrelations.*

```{r, include = FALSE}
saveRDS(time_features_acc, file.path(output_dir, "time_features_acc.rds"))
saveRDS(time_features_gyro, file.path(output_dir, "time_features_gyro.rds"))
```
