```{r, include = FALSE}
source(here::here("setup.R"))
for (file in list.files(here::here("R"), full.names = TRUE)) source(file)
acc_df <- readRDS(file.path(output_dir, "acc_df.rds"))
gyro_df <- readRDS(file.path(output_dir, "gyro_df.rds"))
```

# Time domain features

## Histograms

Histograms give a detailed picture of the distribution of the signal values.
For instance, have a look at the histograms of the signal samples per activity:

```{r}
plot_signal_df_hist <- function(x) {
  x |>
    filter(!is.na(activity)) %>% # keep only labeled samples
    ggplot(aes(X1)) +
    geom_histogram(bins = 40, fill = 1, alpha = 0.5) +
    geom_histogram(aes(X2), bins = 40, fill = 2, alpha = 0.5) +
    geom_histogram(aes(X3), bins = 40, fill = 4, alpha = 0.5) +
    facet_wrap(~activity, scales = "free_y")
}

# Plot a histogram of the accelerometer signal, separated by activity
plot_signal_df_hist(acc_df)
```

```{r}
# Plot a histogram of the gyroscope signal, separated by activity
plot_signal_df_hist(gyro_df)
```

**The histograms for different activities look quite distinct.** This means that statistical summaries
(mean, standard deviation, skewness, etc.) could help us tell the activities apart.

## Features

<details>
<summary>Per axis and magnitude (`*` is `X1`, `X2`, `X3` or `mag`, `dyn_mag`):</summary>

| Feature | Relevance |
|---|---|
| `mean_*`, `median_*` | average signal, direction of gravity, median robust to outliers |
| `sd_*`, `mad_*` | spread of the signal, the second robust to outliers |
| `min_*`, `max_*` | range of movement |
| `q05_*`, `q25_*`, `q75_*`, `q95_*` | shape of the distribution |
| `rms_*` | signal energy |
| `skew_*` | asymmetry of the distribution |
| `kurt_*` | tailedness of the distribution |
| `entropy_*` | uncertainty or randomness of the signal |
| `mean_abs_diff_*`, `max_abs_diff_*` | how abrupt the changes in the signal are |
| `jerk_sd_*` | spread of the jerk (rate of change): how abrupt the movement is |
| `slope_*` | steady trend of the signal |
| `diff_*` | direction of a transition: change from start to end of epoch |
| `half_mean_diff_*` | change in level from the first to the second half of the epoch |
| `half_rms_diff_*` | change in movement from the first to the second half of the epoch |
| `excursion_time_*` | when the largest deviation from the mean occurs (0 = start, 1 = end of epoch) |
| `peaks_*` | share that is local maxima (how oscillatory the signal is) |
| `acf_peak_*` | height of the strongest autocorrelation peak: how regular the rhythm is |
| `acf_peak_lag_*` | lag of that peak in samples: the step period (divide by 50 for seconds) |
| `ar1_*`, `ar2_*`, `ar3_*`, `ar4_*` | autoregression coefficients (Burg, order 4): temporal structure of the signal |

For the magnitude (`*_mag`), these describe the overall movement, regardless of how the phone is oriented.

</details>

<details>
<summary>Per axis only (`*` is `X1`, `X2` or `X3`):</summary>

| Feature | Relevance |
|---|---|
| `zcr_*` | how often the signal crosses its mean |
| `rot_*` | net integral; for gyro, net rotation angle |
| `rot_abs_*` | total amount of movement, regardless of direction |
| `rot_asym_*` | the asymmetry of rotations in each direction |
| `grav_angle_range_*` | how much the angle with gravity varies within the epoch |

</details>

<details>
<summary>Axis compared with the other two (`*` is `X1`, `X2` or `X3`):</summary>

| Feature | Relevance |
|---|---|
| `var_share_*` | how much of the movement is along this axis |
| `grav_angle_*` | angle between axis and gravity |
| `grav_angle_change_*` | change in tilt from start to end of epoch |

</details>

<details>
<summary>All three axes together:</summary>

| Feature | Relevance |
|---|---|
| `sma` | signal magnitude area |
| `mean_jerk`, `sd_jerk`, `rms_jerk` | rate of change |
| `axis_dom` | share of the strongest axis in the overall movement |
| `diff_orient` | orientation change between start and end of signal |
| `axis_angle_X1_X2`, `axis_angle_X1_X3`, `axis_angle_X2_X3` | angle of the mean signal in each plane |

</details>

<details>
<summary>Correlations:</summary>

| Feature | Relevance |
|---|---|
| `acf_*_lag1`, `acf_*_lag2` | correlation of a signal with itself 1 or 2 samples earlier: how smooth it is |
| `cc_X1_X2_lag1`, `cc_X1_X3_lag1`, `cc_X2_X3_lag1` | correlation of one axis with another 1 sample earlier: whether the axes move together |

</details>

## Feature extraction

```{r, fold = "Relevant functions for segmentation of activities", code = readLines(here::here("R", "segmentation.R"))}
source(here::here("R", "segmentation.R"))
```

```{r, fold = "Relevant functions for time domain feature extraction", code = readLines(here::here("R", "features_time.R"))}
source(here::here("R", "features_time.R"))
```

```{r}
# Compute features per epoch for acc
time_features_acc <- get_time_domain_features(acc_df)
head(time_features_acc)

# Compute features per epoch for gyro
time_features_gyro <- get_time_domain_features(gyro_df)
head(time_features_gyro)

# Plot the confidence levels for each activity label
time_features_gyro |>
  filter(aggr_activity != "-") |>
  ggplot(aes(x = aggr_activity, y = activity_confidence)) +
  geom_boxplot() +
  facet_wrap(~aggr_activity, scales = "free_x") +
  theme(axis.text.x = element_blank()) +
  labs(x = "Activity label", y = "Confidence of activity label")
```

This is a tidy data frame that can be used in the classification algorithms discussed in chapters 3 and 4 of ISLR.

***Note**: You may not be familiar with the `acf_*_lag*` and `cc_*_lag*` features computed above.
These are called _autocorrelations_ (at lags 1 and 2) and _lagged cross-correlations_.
They are discussed in [Feature Extraction from Signals](https://paper.dropbox.com/doc/Feature-extraction-from-Signals--A62tmtXDMS34X292NP0fKphQAQ-qCp5uvj47gmyuw5nmB8lL).
They are interesting because slowly changing signals have high autocorellations, while fast changing signals have low or even negative autocorrelations.*

```{r, include = FALSE}
saveRDS(time_features_acc, file.path(output_dir, "time_features_acc.rds"))
saveRDS(time_features_gyro, file.path(output_dir, "time_features_gyro.rds"))
```
