```{r, include = FALSE}
source(here::here("setup.R"))
for (file in list.files(here::here("R"), full.names = TRUE)) source(file)
acc_df <- readRDS(file.path(output_dir, "acc_df.rds"))
gyro_df <- readRDS(file.path(output_dir, "gyro_df.rds"))
```

# Frequency domain features

## Spectrograms

As we looked at histograms of the signal values, we can also look at the spectragrams of the signals.
The spectrum is a representation of the signal in the frequency domain, which can reveal periodic patterns that are not obvious in the time domain.

```{r, fold = "Relevant functions for frequency domain analysis", code = readLines(here::here("R", "utils_frequency.R"))}
source(here::here("R", "utils_frequency.R"))
```

```{r}
plot_signal_df_spectrograms <- function(x) {
  gaussian_sigma <- 3
  x |>
    filter(!is.na(activity)) |>
    group_by(activity) |>
    reframe(
      spec1 = list(compute_spectrum(X1, gaussian_sigma = gaussian_sigma)),
      spec2 = list(compute_spectrum(X2, gaussian_sigma = gaussian_sigma)),
      spec3 = list(compute_spectrum(X3, gaussian_sigma = gaussian_sigma))
    ) |>
    ungroup() |>
    pivot_longer(cols = starts_with("spec"), names_to = "signal", values_to = "spectrum") |>
    unnest(cols = c(spectrum)) |>
    ggplot(aes(x = freq, y = spec, colour = signal)) +
    geom_line() +
    scale_y_log10() +
    facet_wrap(~activity) +
    labs(x = "Frequency", y = "Spectral density (log scale)", colour = "Signal channel")
}

# Plot a spectrogram of the accelerometer signal, separated by activity
plot_signal_df_spectrograms(acc_df)
```

```{r}
# Plot a spectrogram of the gyroscope signal, separated by activity
plot_signal_df_spectrograms(gyro_df)
```

## Converting signals to the frequency domain

Describe a signal in the **frequency domain**.

```{r}
# Compute spectra for each epoch
acc_spect_df <- convert_signal_to_spectrum_df(acc_df)
gyro_spect_df <- convert_signal_to_spectrum_df(gyro_df)
head(acc_spect_df)
```

Now we have a tidy data frame with the spectrum of each signal in each epoch.

# Features

<details>
<summary>Per axis and magnitude (`*` is `X1`, `X2`, `X3` or `mag`, `dyn_mag`):</summary>

| Feature | Relevance |
|---|---|
| `mean_freq_*`, `sd_freq_*` | average and spread of the frequencies |
| `skew_freq_*`, `kurt_freq_*` | asymmetry and tailedness of the spectrum |
| `spec_entropy_*` | how spread out the power is: noise rather than rhythm |
| `edge_freq_*` | frequency below which 90% of the power lies |
| `bin1_*` ... `bin8_*` | share of power in each of 8 bins: finer shape of the spectrum |
| `dom_freq_*` | strongest frequency above 0.5 Hz: the pace of the movement |
| `dom_power_ratio_*` | share of the power at that frequency: how pure the rhythm is |

</details>

## Feature extraction

```{r, fold = "Relevant functions for frequency domain feature extraction", code = readLines(here::here("R", "features_frequency.R"))}
source(here::here("R", "features_frequency.R"))
```

```{r}
# Compute frequency-domain features per epoch for acc
spect_features_acc <- get_frequency_domain_features(acc_spect_df)
head(spect_features_acc)

# Compute frequency-domain features per epoch for gyro
spect_features_gyro <- get_frequency_domain_features(gyro_spect_df)
head(spect_features_gyro)
```

```{r, include = FALSE}
saveRDS(spect_features_acc, file.path(output_dir, "spect_features_acc.rds"))
saveRDS(spect_features_gyro, file.path(output_dir, "spect_features_gyro.rds"))
```
