```{r, include = FALSE}
source(here::here("setup.R"))
for (file in list.files(here::here("R"), full.names = TRUE)) source(file)
sample_labels <- readRDS(file.path(output_dir, "sample_labels.rds"))
```

# Putting it all together

We need to process all of them and combine the resulting data frames in one big data frame.

```{r, fold = "Relevant functions for combining data", code = readLines(here::here("R", "combining.R"))}
source(here::here("R", "combining.R"))
```

```{r}
all_filenames_train <- list(
  "acc" = list.files(train_dir, pattern = "^acc"),
  "gyro" = list.files(train_dir, pattern = "^gyro")
)
all_filenames_test <- list(
  "acc" = list.files(test_dir, pattern = "^acc"),
  "gyro" = list.files(test_dir, pattern = "^gyro")
)
cat("Number of training files:", length(all_filenames_train[["acc"]]), "acc,", length(all_filenames_train[["gyro"]]), "gyro", "\n")
cat("Number of test files:", length(all_filenames_test[["acc"]]), "acc,", length(all_filenames_test[["gyro"]]), "gyro")
```

```{r}
n_samples_per_epoch <- 128
sample_rate <- 50

df_train_acc <- map_dfr(
  all_filenames_train[["acc"]],
  parse_and_features,
  dir = train_dir,
  sample_labels = sample_labels,
  n_samples_per_epoch = n_samples_per_epoch,
  sample_rate = sample_rate,
  .progress = "Parsing all acc training files, gathering features"
)

df_train_gyro <- map_dfr(
  all_filenames_train[["gyro"]],
  parse_and_features,
  dir = train_dir,
  sample_labels = sample_labels,
  n_samples_per_epoch = n_samples_per_epoch,
  sample_rate = sample_rate,
  .progress = "Parsing all gyro training files, gathering features"
)

df_train <- df_train_acc |> inner_join(df_train_gyro, by = c("epoch", "user_id", "exp_id", "sampleid", "n_samples", "aggr_activity", "activity_confidence"))
head(df_train)
```

For predicting on the test set later, we also construct a dataframe for test features.

```{r}
df_test_acc <- map_dfr(
  all_filenames_test[["acc"]],
  parse_and_features,
  dir = test_dir,
  sample_labels = sample_labels,
  n_samples_per_epoch = n_samples_per_epoch,
  sample_rate = sample_rate,
  .progress = "Parsing all acc test files, gathering features"
) |> select(-aggr_activity, -activity_confidence)

df_test_gyro <- map_dfr(
  all_filenames_test[["gyro"]],
  parse_and_features,
  dir = test_dir,
  sample_labels = sample_labels,
  n_samples_per_epoch = n_samples_per_epoch,
  sample_rate = sample_rate,
  .progress = "Parsing all gyro test files, gathering features"
) |> select(-aggr_activity, -activity_confidence)

df_test <- df_test_acc |> inner_join(df_test_gyro, by = c("epoch", "user_id", "exp_id", "sampleid", "n_samples"))
```

## Formatting testing data

Removing unnecessary columns and adding a key column.

```{r}
df_test <- df_test |>
  mutate(
    user_id = paste(ifelse(user_id < 10, "user0", "user"), user_id, sep = ""),
    exp_id = paste(ifelse(exp_id < 10, "exp0", "exp"), exp_id, sep = "")
  ) |>
  unite(Id, user_id, exp_id, sampleid)

df_test <- df_test |> select(-epoch)
cat("Number of rows in test data:", nrow(df_test))
```

## Cleaning training data

Removing rows with NA values.

```{r}
n_na <- sum(is.na(df_train))
cat("Number of NA values:", n_na)
df_train <- df_train |> drop_na()
```

Removing columns unneccessary for fitting.

```{r}
df_train <- df_train |> select(-epoch, -sampleid, -user_id, -exp_id)
```

Checking if there are any linear combinations within features.
Preprocessing data before doing so.

```{r, fold = "Relevant functions for preprocessing", code = readLines(here::here("R", "preprocess.R"))}
source(here::here("R", "preprocess.R"))
```

```{r}
pp <- fit_preprocess(df_train)
df_train_pp  <- apply_preprocess(df_train, pp)
```

```{r}
redundant <- find_redundant_cols(df_train_pp)
cat("Number of linear combinations found:", length(redundant), "\n")
if (length(redundant) > 0) {
  cat("Redundant columns:", paste(redundant, collapse = ", "))
}
# Remove redundant columns from both training and testing data
df_train <- df_train |> select(-all_of(redundant))
df_test <- df_test |> select(-all_of(redundant))
```

## Visualizing features

```{r}
# Too many features now for this viz
# df_train |>
#     filter(activity_confidence > 0) |>
#     pivot_longer(cols = -c(activity_confidence, aggr_activity), names_to = "feature", values_to = "value") |>
#     ggplot(aes(value, color = aggr_activity)) +
#     geom_density() +
#     facet_wrap(~feature, scales = "free")
```

Now the data are turned into a tidy format with features that can be used in any of the algorithms.

```{r, include = FALSE}
saveRDS(df_train, file.path(output_dir, "df_train.rds"))
saveRDS(df_test, file.path(output_dir, "df_test.rds"))
```
