```{r, include = FALSE}
source(here::here("setup.R"))
for (file in list.files(here::here("R"), full.names = TRUE)) source(file)
acc_df <- readRDS(file.path(output_dir, "acc_df.rds"))
gyro_df <- readRDS(file.path(output_dir, "gyro_df.rds"))
```

# Joint frequency and time domain features

The accelerometer measures translation, the gyroscope rotation. Joint features
describe how the two of them relate.

## Features

<details>
<summary>Joint features:</summary>

| Feature | Relevance |
|---|---|
| `cor_acc_gyro_mag` | whether translation and rotation happen together |
| `mean_dot`, `sd_dot` | directional coupling between acceleration and rotation |
| `gyro_acc_rms_ratio` | rotation- vs translation-dominated movement |
| `cor_acc_gyro_X*` | coupling of each accelerometer axis with the same gyroscope axis |

</details>

## Feature extraction

```{r, fold = "Relevant functions for joint feature extraction", code = readLines(here::here("R", "features_joint.R"))}
source(here::here("R", "features_joint.R"))
```

```{r}
# Join the acc and gyro signals of the example recording, sample by sample
joint_df <- join_sensors(acc_df, gyro_df)

# Compute joint features per epoch
joint_features <- get_joint_features(joint_df)
head(joint_features)
```
