```{r, include = FALSE}
source(here::here("setup.R"))
for (file in list.files(here::here("R"), full.names = TRUE)) source(file)
acc_df <- readRDS(file.path(output_dir, "acc_df.rds"))
gyro_df <- readRDS(file.path(output_dir, "gyro_df.rds"))
```

# Gravity frame features

The position and orientation of the phone is different per user and activity.
Gravity features describe the movement of the phone relative to the direction of gravity
(dominant axis), so the features are more user-agnostic.

## Visualization

The scatter plot shows the relationship between the vertical and horizontal components of the acceleration.

```{r, fold = "Relevant functions for gravity frame and features", code = readLines(here::here("R", "utils_gravity.R"))}
source(here::here("R", "utils_gravity.R"))
```

```{r}
plot_grav_df_scatter <- function(x, col1, col2) {
  x |>
    bind_cols(activity = acc_df$activity) |>
    filter(!is.na(activity)) |>
    ggplot(aes(.data[[col1]], .data[[col2]])) +
    geom_point(alpha = 0.1, size = 0.5) +
    facet_wrap(~activity) +
    labs(x = col1, y = col2)
}

grav_df <- gravity_frame(join_sensors(acc_df, gyro_df))

plot_grav_df_scatter(grav_df, "vert", "horiz")
```

```{r}
plot_grav_df_scatter(grav_df, "yaw", "tilt")
```


## Channels

| Channel | Meaning |
|---|---|
| `vert` | acceleration along gravity (vertical) |
| `horiz` | acceleration in the horizontal plane |
| `yaw` | rotation around the gravity axis |
| `tilt` | rotation around a horizontal axis |

## Features

<details>
<summary>Per channel (`*` is `vert`, `horiz`, `yaw` or `tilt`):</summary>

| Feature | Relevance |
|---|---|
| `mean_*`, `median_*`, `sd_*`, `mad_*`, `min_*`, `max_*`, `q05_*`, `q25_*`, `q75_*`, `q95_*`, `rms_*` | size and spread of the movement |
| `skew_*`, `kurt_*`, `entropy_*` | shape of the distribution |
| `mean_abs_diff_*`, `max_abs_diff_*`, `jerk_sd_*` | how abrupt the changes are |
| `slope_*`, `diff_*`, `half_mean_diff_*`, `half_rms_diff_*`, `excursion_time_*` | how the movement develops over the epoch |
| `peaks_*`, `zcr_*`, `acf_peak_*`, `acf_peak_lag_*`, `ar1_*` ... `ar4_*` | rhythm of the movement |
| `rot_*`, `rot_abs_*`, `rot_asym_*` | total movement, and how one-sided it is; on `yaw` this is the net turn |
| `mean_freq_*`, `sd_freq_*`, `skew_freq_*`, `kurt_freq_*`, `spec_entropy_*`, `edge_freq_*`, `bin1_*` ... `bin8_*`, `dom_freq_*`, `dom_power_ratio_*` | the same spectrum features as for the phone axes |

</details>

<details>
<summary>Between the channels - *click to expand*</summary>

| Feature | Relevance |
|---|---|
| `var_share_vert` | how much of the acceleration is vertical |
| `var_share_yaw` | how much of the rotation is turning rather than tipping |
| `dom_acc`, `dom_rot` | how one-sided that split is |
| `sma_acc`, `sma_rot` | overall effort per sensor |
| `mean_jerk_acc`, `sd_jerk_acc`, `rms_jerk_acc`, and the same for `_rot` | rate of change across the channels |
| `cc_<a>_<b>_lag<k>` | correlation of two channels, the second delayed by `k` = 0, 1, 2 samples |

</details>

## Feature extraction

```{r, fold = "Relevant functions for gravity frame feature extraction", code = readLines(here::here("R", "features_gravity.R"))}
source(here::here("R", "features_gravity.R"))
```

```{r}
# Compute the gravity frame features per epoch of the example recording
gravity_features <- get_gravity_features(join_sensors(acc_df, gyro_df))
head(gravity_features)
```
