```{r, include = FALSE}
source(here::here("setup.R"))
for (file in list.files(here::here("R"), full.names = TRUE)) source(file)
df_train <- readRDS(file.path(output_dir, "df_train.rds"))
```


# Model fitting

Training models on the processed training data.

## Define options for training models

Define options for model training, which are used to construct different model configurations.

```{r}
# Define the options for model training
# only use a subset now to save time
opts <- expand_grid(
  method = c("qda", "lda", "naive_bayes"), # "knn", "multinom"
  term_mode = c("nomode", "add", "inter"),
  term = c("noterm", "km_cluster", "km_dist"),
  weighting = c("unweighted", "weighted"),
  pca = c(1, 0.7)
) |>
  # if there's a term but no mode, nothing would happen to it
  filter(!(term_mode == "nomode" & term != "noterm")) |>
  # if there's no term, there's nothing to do with it
  filter(!(term == "noterm" & term_mode != "nomode")) |>
  # only multinom supports weighting
  filter(!(weighting == "weighted" & method != "multinom")) |>
  # qda doesn't work with more features than this
  filter(!(method == "qda" & pca > 0.7)) |>
  filter(!(method == "qda" & term_mode != "nomode")) |>
  # no need for pda lower than 0.95 for models other than qda
  filter(!(method != "qda" & pca < 0.95)) |>
  # this combo takes way too long
  filter(!(term_mode == "inter" & term == "km_dist"))

opts
```

## Training models

```{r, fold = "Relevant functions for preprocessing and constructing data", code = readLines(here::here("R", ".R"))}
source(here::here("R", "data_construct.R"))
```

```{r, fold = "Relevant functions for fitting models", code = readLines(here::here("R", "models.R"))}
source(here::here("R", "models.R"))
```

```{r}
# Set up parallel processing to speed up model fitting
# ==> START LLM https://chatgpt.com/share/6aab8916-1138-83eb-b17f-1e899eec877c
library(doParallel)
n_cores <- parallel::detectCores()
if (!on_kaggle) { n_cores <- n_cores - 1 }
cl <- makePSOCKcluster(n_cores)
registerDoParallel(cl)
# ==> END LLM

# Fit models
fitted_models <- suppressWarnings(fit_all(df_train, opts, number = 5, repeats = 3, nstart = 10))
fitted_models$results

# Clean up parallel processing
stopCluster(cl)
registerDoSEQ()
```

Finding the best model (based on accuracy).

```{r}
best_idx <- which.max(fitted_models$results$accuracy)
best_fit <- list(
  model = fitted_models$models[[best_idx]],
  key = names(fitted_models$models)[[best_idx]],
  pp_utils = fitted_models$pp_utils[[best_idx]]
)

cat("Best model:", best_fit$key, "\n")
```

## Visualizing training results

Visualizing results of different models to see how the "best" model compares to the rest.

```{r}
ggplot(fitted_models$results, aes(x = accuracy, y = kappa)) +
  geom_point(data = fitted_models$results[best_fit$key, ], size = 5) +
  geom_point(aes(color = rownames(fitted_models$results)))
```

```{r}
rs <- resamples(fitted_models$models)
bwplot(rs)
```

```{r, include = FALSE}
saveRDS(best_fit, file.path(output_dir, "best_fit.rds"))
```
