```{r, include = FALSE}
source(here::here("setup.R"))
for (file in list.files(here::here("R"), full.names = TRUE)) source(file)
df_train <- readRDS(file.path(output_dir, "df_train.rds"))
```


# Model fitting

Training models on the processed training data.

## Define options for training models

Define options for model training, which are used to construct different model configurations.

| Method | Purpose |
|---|---|
| `method` | The value of parameter `method` in `caret::train()` |
| `term_mode` | The way using of additional terms in the model ("add" adds terms as predictors, "inter" adds interaction terms) |
| `term` | The additional terms to include in the model |
| `weighting` | Whether to use weighted or unweighted samples (defined by "activity_confidence") |
| `pca` | The proportion of variance to retain in PCA (doesn't apply PCA when `pca` is 1) |
| `corr` | Whether to remove highly correlated features before fitting or not |

We do not include the following options:
- `term_mode`: "add", "inter" because they are expensive to compute. Some show improvements but previous runs showed they're not significant.
- `term`: "km_cluster", "km_dist" as a consequence of the point above.

```{r}
# Define the options for model training
# only use a subset now to save time
opts <- expand_grid(
  method = c("qda", "knn", "naive_bayes", "glmnet", "lda"),
  term_mode = c("nomode"), # + "add", "inter"
  term = c("noterm"), # + "km_cluster", "km_dist"
  weighting = c("unweighted", "weighted"),
  pca = c(1, 0.95, 0.7),
  corr = c("corr", "nocorr")
) |>
  # if there's a term but no mode, nothing would happen to it
  filter(!(term_mode == "nomode" & term != "noterm")) |>
  # if there's no term, there's nothing to do with it
  filter(!(term == "noterm" & term_mode != "nomode")) |>
  # only glmnet supports weighting
  filter(!(weighting == "weighted" & method != "glmnet")) |>
  # qda doesn't work with more features than this
  filter(!(method == "qda" & pca > 0.7)) |>
  filter(!(method == "qda" & term_mode != "nomode")) |>
  # no need for pca lower than 0.95 for models other than qda
  filter(!(method != "qda" & pca < 0.95)) |>
  # glmnet shrinks the coefficients itself, so it has no need for pca
  filter(!(method == "glmnet" & pca < 1)) |>
  # glmnet shrinks correlated features together, so it does better with all of them,
  # while the other methods need the correlated ones removed
  filter((corr == "nocorr") == (method == "glmnet")) |>
  # this combo takes way too long
  filter(!(term_mode == "inter" & term == "km_dist"))

opts
```

## Training models

```{r, fold = "Relevant functions for preprocessing and constructing data", code = readLines(here::here("R", "data_construct.R"))}
source(here::here("R", "data_construct.R"))
```

```{r, fold = "Relevant functions for fitting models", code = readLines(here::here("R", "models.R"))}
source(here::here("R", "models.R"))
```

```{r}
# Set up parallel processing to speed up model fitting
# ==> START LLM https://chatgpt.com/share/6aab8916-1138-83eb-b17f-1e899eec877c
library(doParallel)
cl <- makePSOCKcluster(n_cores())
registerDoParallel(cl)
# ==> END LLM

# Fit models
fitted_models <- suppressWarnings(fit_all(df_train, opts, number = 10, repeats = 5, nstart = 10))
fitted_models$results

# Clean up parallel processing
stopCluster(cl)
registerDoSEQ()
```

Finding the best model (based on accuracy).

```{r}
best_idx <- which.max(fitted_models$results$accuracy)
best_fit <- list(
  model = fitted_models$models[[best_idx]],
  key = names(fitted_models$models)[[best_idx]],
  pp_utils = fitted_models$pp_utils[[best_idx]]
)

cat("Best model:", best_fit$key, "\n")
```

## Visualizing training results

Visualizing results of different models to see how the "best" model compares to the rest.

```{r}
ggplot(fitted_models$results, aes(x = accuracy, y = kappa)) +
  geom_point(data = fitted_models$results[best_fit$key, ], size = 5) +
  geom_point(aes(color = rownames(fitted_models$results)))
```

```{r}
# Extract the fold statistics for each model
rs <- resamples(fitted_models$models)
# box-and-whisker plot for the performance distribution
bwplot(rs)
```

```{r}
# Compute the table of pairwise comparisons
summary(diff(rs))
```

```{r, include = FALSE}
saveRDS(best_fit, file.path(output_dir, "best_fit.rds"))
```
